Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-07-14 main.tex
correct my name
vince corrections

% Title
\title{Reinforcement Learning Produces Dominant Strategies for the
Iterated Prisoner's Dilemma}
\author{Marc Harper \and
        Vincent Knight \and
        Martin Jones \and
        Georgios Koutsovoulos \and
        Nikoleta Glynatsi \and
        Owen Campbell}
\date{}

@@

\begin{abstract}
    We present tournament results and several powerful strategies for the Iterated
    Prisoner's Dilemma created using reinforcement learning techniques
    (evolutionary and particle swarm algorithms). These strategies are
    trained to perform well against a corpus of over 170 distinct
    opponents, including many well-known and classic strategies. All
    the trained strategies win standard tournaments against the total collection
    of other opponents. The trained strategies and one particular human made
    designed strategy are the top performers in tournaments where also noise is introduced.
\end{abstract}

@@

The strategies that win the most matches
(Table~\ref{tbl:standard_wins_top_winners}) are Defector~\cite{Axelrod1984} and Aggravater~\cite{axelrodproject}, followed
by handshaking and zero determinant strategies~\cite{Press2012}. 
This includes two handshaking
strategies that were the result of training to maximize Moran process fixation
(TF1 and TF2). No strategies were trained specifically to win matches. None of
the top scoring strategies appear in the top 15 list of strategies ranked by
match wins. This can be seen in Figure~\ref{fig:standard_winplot} where the
distribution of the number of wins of each strategy is shown.

>>>>

% Title
\title{Reinforcement Learning Produces Dominant Strategies for the
Iterated Prisoner's Dilemma}
\author{Marc Harper \and
        Vincent Knight \and
        Martin Jones \and
        Georgios Koutsovoulos \and
        Nikoleta E. Glynatsi \and
        Owen Campbell}
\date{}

@@

\begin{abstract}
    We present tournament results and several powerful strategies for the Iterated
    Prisoner's Dilemma created using reinforcement learning techniques
    (evolutionary and particle swarm algorithms). These strategies are
    trained to perform well against a corpus of over 170 distinct
    opponents, including many well-known and classic strategies. All
    the trained strategies win standard tournaments against the total collection
    of other opponents. The trained strategies and one particular human made
    designed strategy are the top performers in noisy tournaments also.
\end{abstract}

@@

The strategies that win the most matches
(Table~\ref{tbl:standard_score}) are Defector~\cite{Axelrod1984} and Aggravater~\cite{axelrodproject}, followed
by handshaking and zero determinant strategies~\cite{Press2012}. 
This includes two handshaking
strategies that were the result of training to maximize Moran process fixation
(TF1 and TF2). No strategies were trained specifically to win matches. None of
the top scoring strategies appear in the top 15 list of strategies ranked by
match wins. This can be seen in Figure~\ref{fig:standard_winplot} where the
distribution of the number of wins of each strategy is shown.
